Title

### 2018-07-31 thesis/paper/paper.tex
Moved single best value to correct position
Added One-of qualifier value

>>>>

\subsection{One-of qualifier value (Q52712340)}
The one-of qualifier value constraint is violated if a constrained statement has a qualifier with a value unequal to all allowed values. Inequality needs to be pre-processed between all values of qualifiers on constrained statements. With the set of allowed Values \(A\) the rules are
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{qualifierEDB}(S, \text{qualifierProperty}, O) \wedge \text{unequal}(\{A\}, O)
\end{split}
\end{equation*}
